Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-14 analysis/paper/paper.Rmd
Flesh out idea more about invited articles being no different

The methods for selecting articles meant that only page numbers between 1 and 150 were selected.
This approach assumed that there was no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year and some journals, e.g., *Phytopathology*® have focus issues with invited authors.
In spite of some publications being from special issues, there were no detectable differences in the reproducibility of the articles as defined and measured by this article, so the assumption appears to be correct.

>>>>

The methods for selecting articles meant that only page numbers between 1 and 150 were selected.
This approach assumed that there was no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year and some journals, e.g., *Phytopathology*® have focus issues with invited authors.
In spite of some publications being from special issues, there were no detectable differences in the reproducibility of the articles as defined and measured by this article, so the assumption appears to be correct and more importantly, may show that even when authors are specifically recruited that they are no more likely to share the supporting materials for the articles that they write.
